Super awesome embeddings

### 2019-02-03 paper/main.tex
Add examples for csv files

@@

\textit{"Sulfur- and oil-soaked materials were sometimes ignited and thrown at the enemy, or attached to spears, arrow and
*bolts* and fired by hand or machine. Some siege techniques—such as mining and boring—relied on combustibles and
fire to complete the collapse of walls and structures."}

\bigskip
The correct keyword for each example, together with a path to file and a link, where the original text was taken from, are stored in CSV files: \textit{train.csv} for training set, \textit{test.csv} for test set (columns: path,keyword,link).
Keywords themselves, together with links to their Wikipedia articles, are stored in \textit{keywords.csv} file.
Dataset, together with the code to execute experiments from this paper, can be found on our GitHub repository \cite{repository}.

>>>>

The correct keyword for each example, together with a path to file and a link, where the original text was taken from, are stored in CSV files: \textit{train.csv} for training set, \textit{test.csv} for test set (columns: path,keyword,link).
Keywords themselves, together with links to their Wikipedia articles, are stored in \textit{keywords.csv} file.
Dataset, together with the code to execute experiments from this paper, can be found on our GitHub repository \cite{repository}.

@@

\smallskip
\textbf{Keyword definition}: keyword.csv\newline
\textit{
keyword,link\newline
...\newline
bolt crossbow,https://en.wikipedia.org/wiki/Crossbow\_bolt\newline}

\smallskip
\textbf{Test set}: test.csv\newline
\textit{
path,keyword,link\newline
...\newline
texts/test/bolt\_crossbow\_5.txt,bolt crossbow,https://en.wikipedia.org/wiki/Incendiary\_device\newline
}

\smallskip
\textbf{Text}: texts/test/bolt\_crossbow\_5.txt\newline
\textit{"Sulfur- and oil-soaked materials were sometimes ignited and thrown at the enemy, or attached to spears, arrow and *bolts* and fired by hand or machine. Some siege techniques—such as mining and boring—relied on combustibles and fire to complete the collapse of walls and structures."}
